A continuous urbanization index to assess phylogenetic adaptations in urban bird living

### 2018-05-07 ms.Rmd
some latex formatting

author: | 
  | Corey T. Callaghan^[Corresponding author: c.callaghan@unsw.edu.au] $^1$, Richard E. Major $^1$$^,$$^2$, John H. Wilshire $^1$, John M. Martin $^1$$^,$$^3$, Richard T. Kingsford $^1$, William K. Cornwell $^1$$^,$$^4$
  | $^1$Center for Ecosystem Science, School of Biological, Earth and Environmental Sciences, UNSW Sydney, Sydney, NSW, Australia; $^2$Australian Museum Research Institute, Sydney, NSW, Australia; $^3$Royal Botanic Gardens and Domain Trust, Sydney, NSW, Australia; $^4$Evolution and Ecology Research Centre, School of Biological, Earth and Environmental Sciences, UNSW Sydney, Sydney, NSW, Australia
date: ""
output:
  pdf_document: null
  bookdown::word_document2: null
  bookdown::tufte_html2:
    number_sections: no
    toc: no
  html_document:
    df_print: paged
    toc: no
fontsize: 12pt
link-citations: no
csl: https://raw.githubusercontent.com/citation-style-language/styles/master/ecology-letters.csl
bibliography: references.bib
header-includes: 
  - \usepackage{setspace}\doublespacing
  - \usepackage{lineno}
  - \linenumbers
---

@@

# Tables
```{r Table 1, echo=FALSE, warning=FALSE, message=FALSE}
library(readr)
Table1 <- read_csv("Data/Table1.csv")

@@

kable(Table1, format = "latex", caption = "Results showing the significance of the phylogenetic signal analyses.", booktabs = T) %>%
kable_styling(latex_options = c("striped", "hold_position"))

@@

kable(collinearity_investigation, format = "latex", caption = "Variance inflation factors for the explanatory variables used in the analysis.", booktabs = T) %>%
kable_styling(latex_options = c("striped", "hold_position"))

@@

kable(TableS2, format = "latex", caption = "Summary statistics of the phylogenetic signal analysis.", booktabs = T) %>%
kable_styling(latex_options = c("striped", "hold_position"))
```

>>>>

author: | 
  | Corey T. Callaghan^[Corresponding author: c.callaghan@unsw.edu.au] $^1$, Richard E. Major $^1$$^,$$^2$, John H. Wilshire $^1$, John M. Martin $^1$$^,$$^3$, Richard T. Kingsford $^1$, William K. Cornwell $^1$$^,$$^4$
  | $^1$Center for Ecosystem Science, School of Biological, Earth and Environmental Sciences, UNSW Sydney, Sydney, NSW, Australia; $^2$Australian Museum Research Institute, Sydney, NSW, Australia; $^3$Royal Botanic Gardens and Domain Trust, Sydney, NSW, Australia; $^4$Evolution and Ecology Research Centre, School of Biological, Earth and Environmental Sciences, UNSW Sydney, Sydney, NSW, Australia
date: ""
output:
  rmarkdown::pdf_document:
    fig_caption: yes    
    includes:  
      in_header: preamble-latex.tex
fontsize: 12pt
link-citations: no
csl: https://raw.githubusercontent.com/citation-style-language/styles/master/ecology-letters.csl
bibliography: references.bib

---

@@

# Tables

```{r Table 1, echo=FALSE, warning=FALSE, message=FALSE}
library(readr)
Table1 <- read_csv("Data/Table1.csv")

@@

kable(Table1, format = "latex", caption = "Results showing the significance of the phylogenetic signal analyses.", booktabs = T) %>%
kable_styling(latex_options = c("hold_position"))

@@

kable(collinearity_investigation, format = "latex", caption = "Variance inflation factors for the explanatory variables used in the analysis.", booktabs = T) %>%
kable_styling(latex_options = c("hold_position"))

@@

kable(TableS2, format = "latex", caption = "Summary statistics of the phylogenetic signal analysis.", booktabs = T) %>%
kable_styling(latex_options = c("hold_position"))
```
